---
title: "R-ggridges"
date: "Last compiled on `r format(Sys.time(), '%c, %Z')`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning = FALSE)
```

## R-ggridges Introduction with `geom_density_ridges()`

### Load the data

```{r}

# library
library(tidyverse)
library(ggridges) # Ridgeline Plots in ggplot2
library(ggplot2)
(diamonds)
```

### Visualization part

#### Basic plot

```{r}

diamonds %>% 
  ggplot(aes(x = price, y = cut, fill = cut))+
  geom_density_ridges()+
  theme_ridges()+
  theme(legend.position = 'none')

```

> Ideal cuts do not neccessarily have higher price. Why is that? Shouldn't that be the better cuts, the higher price?
A: "Ideal" does not mean the best?

#### Change to histogram with `stat='binline', bins=22, alpha=0.6`

```{r}
diamonds %>% 
  ggplot(aes(x = price, y = cut, fill = cut))+
  geom_density_ridges(alpha=.6, stat = 'binline', bins=22)+
  theme_ridges()+
  theme(legend.position = 'none')
  
  
```

#### Facet by the third variable (`facet_wrap()`)

```{r}
diamonds %>% 
  ggplot(aes(x = price, y = cut, fill = cut))+
  geom_density_ridges(alpha=.6)+
  facet_wrap(~color)+
  theme_ridges()+
  theme(legend.position = 'none')+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


```

#### Add statistical measurements (quantiles) by `quantile_lines = TRUE`

```{r}

diamonds %>% 
  ggplot(aes(x = price, y = cut, fill = cut))+
  geom_density_ridges(alpha=.7, quantile_lines = TRUE)+
  theme_ridges()+
  theme(legend.position = 'none')


```

```{r}




```





